\documentclass[xcolor=dvipsnames]{beamer}

\usetheme{Antibes}
\usecolortheme[named=Maroon]{structure}
\begin{document}

\begin{frame}
	\begin{center}
		\huge HP Capstone \\
        Big Data Analytics \\
        \small Prepared by: \\
        Nic Desilets, \\
        James Stallkamp, \\
        Nathaniel Whitlock
	\end{center}
\end{frame}

\begin{frame}
	\textbf{Introduction} \\
    The following slides will be an overview of the individual experiences of each of the members of our senior design group.
    They be organized by individual in the order of; Nic Desilets, James Stallkamp, and Nathaniel Whitlock.
\end{frame}

%% Nic's Section
\begin{frame}
	\begin{center}
		\huge Nic's Experience
    \end{center}
\end{frame}

\begin{frame}
\begin{itemize}
	\item \textbf{Weeks 0-2}
    \begin{itemize}
  		\item Introduction to the class and what it entails.
        \item Introduced to some of this year's capstone projects and their sponsors.
        \item Read over the complete list of available projects.
        \item Was primarily interested in web related projects.
        
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
    \item \textbf{Week 3}
    \begin{itemize}
  	    \item Got on board with HP Big Data Analytics.
        \item Initial meeting went over project details and expectations.
        \item Discussed a little bit about Oracle Database 12c.
        \item Core problem: 72-core, 3TB server not being fully utilized.
        \item Established a regular weekly meeting time.
        \item Began problem statement document.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
    \item \textbf{Week 4}
    \begin{itemize}
  	    \item Established weekly meeting time with TA.
  	    \item Tried to get Oracle Database 12c installed prior to the next HP meeting.
  	    \item Although the install was successful, the database itself was not correctly configured.
  	    \item Spent a fair amount of time installing and setting up Oracle 12c with help from our clients.
  	    \item Began discussing the dynamic performance views in the database.
  	    \item Goal for next meeting was to begin designing the toolkit.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
    \item \textbf{Week 5}
    \begin{itemize}
  	    \item Spent some time this week revising our problem statement document.
  	    \item Removed some technical jargon from it.
  	    \item Had a better idea of what our target audience would be.
  	    \item Started working on the requirements document.
  	    \item Reinstalled Oracle 12c and got it configured properly.
  	    \item Got set up with HP's test server and database.
    \end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
	\item \textbf{Week 6}
    \begin{itemize}
    	\item Struggled a bit with the requirements document.
    	\item The requirements for the document did not quite fit our project.
    	\item Was pretty busy during this week due to midterms.
    	\item Setup a Slack channel for our group to help improve communications.
   		\item Email is fine but not quite suited for instant messaging.
   		\item Started reading Explain the Explain Plan document.
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
	\item \textbf{Week 7}
   	\begin{itemize}
    	\item Read over the Explain the Explain Plan document.
    	\item Got a little more insight into the internals of the database.
    	\item We were given a script to generate a set of data that is similar to the real data set.
    	\item Talked a little bit more about the dynamic performance views.
    	\item Discussed different IDEs, toolkits, and partitioning types.
    	\item Goal before next meeting was to continue familiarizing ourselves with Oracle 12c (V\$, X\$).
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
	\item \textbf{Week 8}
    \begin{itemize}
    	\item A lot of time was spent on the tech. review early on in the week.
    	\item Ensure that assignment requirements were appropriately met, finalizing.
    	\item This week's meeting with our client was one of the most productive.
    	\item Wasn't tied down with worrying about another paper.
    	\item Was able to start formulating queries to query different V\$ tables.
    	\item Constructed sequence of queries to obtain database times for each parallel executor.
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
	\item \textbf{Week 9}
    \begin{itemize}
    	\item Struggled with getting a start on the design document.
    	\item While other papers were difficult, this one seemed the most difficult.
    	\item Seemed way overkill for our toolkit that we're designing.
    	\item We continued to make more progress on obtaining metrics information during our weekly meeting.
    	\item Main goal at this point was to continue working on the design document.
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
	\item \textbf{Week 10}
    \begin{itemize}
    	\item This week was primarily working on and completing the design document.
    	\item Definitely one of the more difficult papers, but we got it done.
    	\item Got introduced to tracing during our weekly meeting.
    	\item Verbose logging of what exactly the database is doing.
    	\item Helps determine how the optimizer is coming up with its execution plans.
    	\item Can be used in conjunction with dynamic performance views.
    	\item Main goal was to compile our blog reports into our progress report document and presentation.
	\end{itemize}
\end{itemize}
\end{frame}

%% James' Section
\begin{frame}
	\begin{center}
		\huge James' Experience
    \end{center}
\end{frame}

\begin{frame}
\begin{itemize}
	\item \textbf{Weeks 0-3}
	\item During the first three weeks we were introduced to   the structure of our capstone project.
    \item We heard project proposals from clients and voted on the ones we preferred to work with. 
    \item I was assigned to work with HP's big data project.
    \item In week three we had the initial meeting with our client, which went well.
    \item We spent the meeting getting a basic understanding of the project. Which is that HP has a very powerful server that seems to be under utilizing its resources.
    \item Personally I have concerns because I have very little experience with databases but this presents a good opportunity to learn.
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
	\item \textbf{Week 4}
    \begin{itemize}    	
        \item This week the rest of my group began to setup the software packages on their personal laptops
        \item I don't own a laptop so I took notes and repeated the process on my desktop.
         \item I discussed with our mentors how important it would be to have a laptop, and I will try to find one to use or borrow.
        
        \item Began revision on Problem Statement based on feedback
        \item Discussed method of retrieving metrics from dynamic performance views
        \item Missed TA meeting. I completely forgot about and missed the TA meeting. Moving forward I will be better about  attending meetings. 
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
	\item \textbf{Week 5}
    \begin{itemize}
    	\item I confirmed I have a laptop to borrow, and I will be driving to Portland this weekend to pick it up from my parents.
        \item I have successfully set up SQL developer on my personal desktop and will do so on the laptop next week.
    \end{itemize}
   	\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
	\item \textbf{Week 6}
    \begin{itemize}
    	\item Spent most of the time working on the requirements document.
        \item As a group we had issues coordinating for this document and largely worked on it in individual segments.
        \item I have the weakest skills with Latch and Nathaniel and Nic are doing most of the formatting. This is something I will need to work on.
        \item For next weeks meeting we all will be reading Explain the Explain plan which will explain how Oracle databases execute and optimize queries. 
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
	\item \textbf{Week 7}
   	\begin{itemize}
    	\item For the meeting this week we all read Explain the Explain plan, then discussed it.
        \item The document does into detail on how a sql query is executed as well as optimized.
        \item We learned about the various internal tables on Oracle SQL databases, and which contain useful performance data. 
        \item I am still having issues with my personal machine the VM that I set up keeps crashing or corrupting the image when I try to resume a session.
        \item Still having issues with my virtual box image not loading when I try to resume, will plan on talking to Andy next meeting to fix this. 
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
	\item \textbf{Week 8}
    \begin{itemize}
    	
        \item Spent time this week working on my section of the tech review. 
        \item My section to research is which IDE which we will be using. 
        \item Our mentors have introduced us to SQL developer which is what we will probably use but I will research SQL plus as well as TOAD as alternatives
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
	\item \textbf{Week 9}
    \begin{itemize}
    	\item Spent most of our time this week working on the Design document.
        \item This document proved to be very difficult to write because our project is researched based.
        \item Missed Weekly HP meeting because I was sick.
        \item After having continued trouble with my virtual machine I have decided that when I am at HP I will use the test server they have provided and at home I will use the server on my Desktop.
        \item For some reason I can not seem to maintain the integrity of the image in the virtual machine on my laptop work
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
	\item \textbf{Week 10}
    \begin{itemize}
    	\item The weekly meeting was focused on understanding how tracing works. 
        \item We started the time line for our progress report but did not accomplish much.
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
	\begin{center}
		\huge Nathaniel's Experience
    \end{center}
\end{frame}

%% Nate's Section
\begin{frame}
\begin{itemize}
\item \textbf{Weeks 0-3}
	\begin{itemize}
    	\item Prior to Group Assignment
    	\begin{itemize}
          \item Learning about structure of our course
          \item Read about available projects
          \item Spoke with client about getting involved in their project
          \item Voted on projects of interest and assigned to group
          \end{itemize}
         \item Post Group Assignment
     	 \begin{itemize}
          	\item Initial meeting with client
            \item Learned about the scope of our problem
            \item Learned about some Oracle specific database concepts
            \item Scheduled remained of meeting times for the term
            \item Began working on Problem Statement document
          \end{itemize}
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
	\item \textbf{Week 4}
    \begin{itemize}
    	\item Getting software installed on person computers
        \begin{enumerate}
        	\item Issues with package dependencies
            \item Network limitations due to HP firewall
            \item Configuration issues with Oracle environment and listener
        \end{enumerate}
        \item Began revision on Problem Statement based on feedback
        \item Discussed method of retrieving metrics from dynamic performance views
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
	\item \textbf{Week 5}
    \begin{itemize}
    	\item Swapped from personal computer use to work laptop
        \item Finished installing required software on work laptop
        \item Dealt with network issues from within virtual machine
        \item Began working on the Requirements Document
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
	\item \textbf{Week 6}
    \begin{itemize}
    	\item Majority of time spent on finishing the Requirements Document
        \item Hard to find time to work in concert on the Requirement Document
        \item Began executing queries against dynamic performance views on personal computer
        \item Ran into major issues forcing formatting on \LaTeX \ class file
        \begin{itemize}
        	\item T.A. helped point me in the right direction
            \item \textbf{Lesson learned:} Don't try to force formatting changes on a class file
        \end{itemize}
     	\item Began reading Oracle white paper
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
	\item \textbf{Week 7}
   	\begin{itemize}
		\item Discussed the Explain Plan white paper
        \item \textbf{Issues encountered:}
        \begin{itemize}
        	\item Forgot password to personal 12c environment
        \end{itemize}
        \item Provided PL/SQL script to generate data
        \item Emphasis on learning more about dynamic performance views
        \item Began the partition of work for the Technology Review, my areas of focus included:
        \begin{itemize}
        	\item Partitioning
            \item Parallelism
        \end{itemize}
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
	\item \textbf{Week 8}
    \begin{itemize}
    	\item The majority of efforts were spent on finalizing Technology Review
        \item Unsure about initial feedback from document
        \item Began initial efforts on outlining the Design Document
        \item No real progress on toolkit development
        \item Meeting with clients becoming increasing focused on development
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
	\item \textbf{Week 9}
    \begin{itemize}
    	\item Further pushing into pre-toolkit development process
        \item Majority of efforts placed on finishing portion of design document
        \item News from client about Oracle convention
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
	\item \textbf{Week 10}
    \begin{itemize}
    	\item Began focusing on the topic of tracing
        \item Experimented with Oracle native tools for trace file analysis
        \item Began focusing on creating a time line of progress over the term
	\end{itemize}
\end{itemize}
\end{frame}

\begin{frame}
	\textbf{Conclusion} \\
   	\begin{itemize}
    	\item Majority of the term was spent on writing documentation
        \item We have hope that this will guide us in development
        \item Issues with software installation
        \item Benefit of our experienced mentors
        \item Plan moving forward
        
    \end{itemize}
\end{frame}

\end{document}
